Promotors' reports on the first draft of the thesis document.

### 2020-05-21 ChapterPreliminaries/ChapterPreliminaries.tex
Final final version before internal defense

With a step input ${u} = \bar{{u}} s$, where $s(k) = 1$, for $k \geq 0$, and $s(k) = 0$, for $k < 0$, the discrete-time state-space representation of the LTI sensor is equivalent to an augmented autonomous system  
\begin{equation} \begin{aligned} \mathbf{x}_\text{a}(k+1) &= \underbrace{ \begin{bmatrix} \mathbf{A} & \mathbf{B} \\ 0 & 1 \end{bmatrix} }_{\mathbf{A}_\text{a}} \mathbf{x}_\text{a}(k) , \quad \text{where} \ \ \mathbf{x}_\text{a}(k) = \begin{bmatrix} \mathbf{x}(k) \\ {u}(k) \end{bmatrix}, \ \ \mathbf{x}_{\text{ini}} = \mathbf{x}(0) \\
{y}(k) &= \underbrace{ \begin{bmatrix} \mathbf{C} & \mathbf{D} \end{bmatrix} }_{\mathbf{C}_\text{a}} \mathbf{x}_\text{a}(k) . \label{eqn:augmented} \end{aligned} \end{equation}
The eigenvalues $\lambda$ of the augmented autonomous system are found using
\[ \left| \lambda \mathbf{I} - \mathbf{A}_\text{a} \right| = \left| \lambda \mathbf{I} - \begin{bmatrix} \mathbf{A} & \mathbf{B} \\ 0 & 1 \end{bmatrix} \right| = \left| \lambda \mathbf{I} - \mathbf{A} \right| \left( \lambda - 1 \right) = 0.\]
Therefore, the eigenvalues, poles, of the augmented autonomous system (\ref{eqn:augmented}) are the eigenvalues, poles, of the LTI system, with the additional eigenvalue $\lambda = 1$, pole at $(1,0)$.

@@

A third method can directly estimate the input step level from the step response, without the identification of a sensor model.
Applying the first difference operator, $\Delta = \sigma - 1$, to the system state-space representation (\ref{eqn:dtsslti}), we have
\begin{equation} \begin{aligned} \Delta \mathbf{x}(k+1) = \mathbf{A} \Delta \mathbf{x}(k), \quad \Delta {y}(k) = \mathbf{C} \Delta \mathbf{x}(k), \quad \text{with} \quad \Delta \mathbf{x}_{\text{ini}} = \Delta \mathbf{x}(0) , \label{eqn:ssalti} \end{aligned} \end{equation}
where $\sigma$ is the shift operator, defined as $(\sigma^\tau y) (k) = y(k + \tau)$, and
$\Delta {u}(k) = \mathbf{0}$, for $k \geq 0$, and
$\Delta \mathbf{x}(0) = (\mathbf{A} - \mathbf{I}) \mathbf{x}(0) + \mathbf{B} \bar{{u}}$.
The resulting system (\ref{eqn:ssalti}) is autonomous.
When the response $\Delta {y}$ is persistingly exciting of order $L$, i.e., when the rank of the Hankel matrix $\mathbfcal{H}_{L+1}(\Delta {y})$ of $L+1$ block rows constructed from $\Delta {y}$ satisfies
\begin{equation} \mathrm{rank} \left( \mathbfcal{H}_{L+1} \left( \Delta {y} \right) \right) \leq L,  \end{equation}
the Hankel matrix $\mathbfcal{H}_{L+1}(\Delta {y})$ provides a linear map to the free responses of the augmented autonomous system (\ref{eqn:augmented}).  
In this case, the total response of the system is given by 
\[ \mathbf{y} = G \ \bar{{u}} + \mathbfcal{H}(\Delta {y}) \ \bm\ell} \]
that is equivalent to
\begin{equation} \underbrace{ \begin{bmatrix} y(n+1) \\ \vdots \\ y(T) \end{bmatrix}}_{\mathbf{y}} = \underbrace{ \begin{bmatrix} G & \Delta y(1) & \Delta y(2) & \cdots & \Delta y(n) \\ G & \Delta y(2) & \Delta y(3) & \cdots & \Delta y(n+1) \\ \vdots & \iddots & \iddots & \iddots \\ G & \Delta y(T-n) & \Delta y(T-n+1) & \cdots & \Delta y(T-1) \end{bmatrix}}_{\mathbf{K}} \underbrace{ \begin{bmatrix} \bar{{u}} \\ \bm{\ell} \end{bmatrix} }_{\bm{\theta}} , \label{eqn:ddsiemexd} \end{equation}
where $T$ is the number of samples, and the vector $\bm{\ell}$ is a linear transformation of the system initial conditions \citep{Markovsky15cep}.  
The solution to this system of equations exist and is unique when we have exact data.
Nevertheless, in the practice, the observations of the sensor step response are perturbed by noise.

>>>>

With a step input ${u} = \bar{{u}} s$, where $s(k) = 1$, for $k \geq 0$, and $s(k) = 0$, for $k < 0$, the discrete-time state-space representation of the LTI sensor is equivalent to an augmented autonomous system  
\begin{equation} \begin{aligned} \mathbf{x}_\text{a}(k+1) &= \underbrace{ \begin{bmatrix} \mathbf{A} & \mathbf{B} \\ 0 & 1 \end{bmatrix} }_{\mathbf{A}_\text{a}} \mathbf{x}_\text{a}(k) , \quad \text{where} \ \ \mathbf{x}_\text{a}(k) = \begin{bmatrix} \mathbf{x}(k) \\ {u}(k) \end{bmatrix}, \ \ \mathbf{x}_{\text{ini}} = \mathbf{x}(0) \\
{y}(k) &= \underbrace{ \begin{bmatrix} \mathbf{C} & D \end{bmatrix} }_{\mathbf{C}_\text{a}} \mathbf{x}_\text{a}(k) . \label{eqn:augmented} \end{aligned} \end{equation}
The eigenvalues $\lambda$ of the augmented autonomous system are found using
\[ \left| \lambda \mathbf{I} - \mathbf{A}_\text{a} \right| = \left| \lambda \mathbf{I} - \begin{bmatrix} \mathbf{A} & \mathbf{B} \\ 0 & 1 \end{bmatrix} \right| = \left| \lambda \mathbf{I} - \mathbf{A} \right| \left( \lambda - 1 \right) = 0.\]
Therefore, the eigenvalues, poles, of the augmented autonomous system (\ref{eqn:augmented}) are the eigenvalues, poles, of the LTI system, with the additional eigenvalue $\lambda = 1$, pole at $(1,0)$.

@@

A third method can directly estimate the input step level from the step response, without the identification of a sensor model.
Applying the first difference operator, $\Delta = \sigma - 1$, to the system state-space representation (\ref{eqn:dtsslti}), we have
\begin{equation} \begin{aligned} \Delta \mathbf{x}(k+1) = \mathbf{A} \Delta \mathbf{x}(k), \quad \Delta {y}(k) = \mathbf{C} \Delta \mathbf{x}(k), \quad \text{with} \quad \Delta \mathbf{x}_{\text{ini}} = \Delta \mathbf{x}(0) , \label{eqn:ssalti} \end{aligned} \end{equation}
where $\sigma$ is the shift operator, defined as $(\sigma^\tau y) (k) = y(k + \tau)$, and
$\Delta {u}(k) = \mathbf{0}$, for $k \geq 0$, and
$\Delta \mathbf{x}(0) = (\mathbf{A} - \mathbf{I}) \mathbf{x}(0) + \mathbf{B} \bar{{u}}$.
The resulting system (\ref{eqn:ssalti}) is autonomous.
When the response $\Delta {y}$ is persistently exciting of order $L$, i.e., when the rank of the Hankel matrix $\mathbfcal{H}_{L+1}(\Delta {y})$ of $L+1$ block rows constructed from $\Delta {y}$ satisfies
\begin{equation} \mathrm{rank} \left( \mathbfcal{H}_{L+1} \left( \Delta {y} \right) \right) \leq L,  \end{equation}
the Hankel matrix $\mathbfcal{H}_{L+1}(\Delta {y})$ provides a linear map to the free responses of the augmented autonomous system (\ref{eqn:augmented}).  
In this case, the total response of the system is given by 
\begin{equation*} \mathbf{y} = G \bar{u} + \mathbfcal{H}\left(\Delta {y}\right) \bm{\ell} \end{equation*}
that is equivalent to
\begin{equation} \underbrace{ \begin{bmatrix} y(n+1) \\ \vdots \\ y(T) \end{bmatrix}}_{\mathbf{y}} = \underbrace{ \begin{bmatrix} G & \Delta y(1) & \Delta y(2) & \cdots & \Delta y(n) \\ G & \Delta y(2) & \Delta y(3) & \cdots & \Delta y(n+1) \\ \vdots & \iddots & \iddots & \iddots \\ G & \Delta y(T-n) & \Delta y(T-n+1) & \cdots & \Delta y(T-1) \end{bmatrix}}_{\mathbf{K}} \underbrace{ \begin{bmatrix} \bar{{u}} \\ \bm{\ell} \end{bmatrix} }_{\bm{\theta}} , \label{eqn:ddsiemexd} \end{equation}
where $T$ is the number of samples, and the vector $\bm{\ell}$ is a linear transformation of the system initial conditions \citep{Markovsky15cep}.  
The solution to this system of equations exist and is unique when we have exact data.
Nevertheless, in the practice, the observations of the sensor step response are perturbed by noise.
